---
title: "00_metadata_selection"
format: md
editor: visual
---

```{r, echo = F}
library(tidyverse)
# library(kableExtra)

library(rvest, warn.conflicts=FALSE)
library(xml2)
```

# Load data

```{r}
fl <- list.files(path = "../metadata/catalogue_export/",
                 full.names = T)
print(paste0("Number of authors exported from gallica metadata: ", length(fl)))

fl
```

Read each table in a loop and bind the rows together

```{r}

x <- NULL
df <- NULL

for (i in 1:length(fl)) {
  x <- read.csv(fl[i], sep = ";")
  
  x <- x %>% 
    select(-n..notice.BnF, -Localisation, 
           -Exemplaire.n., -Couverture, -X) %>% 
    distinct()
  
  df <- rbind(df, x)
}

glimpse(df)
```

```{r}
# missed Fauchet data
f <- read.csv("../metadata/catalogue_export/fauchet.csv", sep = ";")
df <- f %>% 
    select(-n..notice.BnF, -Localisation, 
           -Exemplaire.n., -Couverture, -X) %>% 
    distinct()

glimpse(df)
```

Number of books found for each author:

```{r}
df %>% count(Auteur, sort = T) %>% head(10)
```

## Filter authors

Read the file with a list of authors' names as they are in Gallica

```{r}
n <- read_file("../metadata/bnf_authors.txt") # read the list
n <- unlist(str_split(n, "\n"))

head(n)
```

Save list with \| collapse for use in regex

```{r}
authors <- paste0(n, collapse = "|")
authors
```

Select rows that doesn't have multiple authors (no \| separator) & written by one of the selected authors:

```{r}
nrow(df)

df_cln <- df %>% 
  filter(!str_detect(Auteur, "\\|")) %>% 
  filter(str_detect(Auteur, authors)) %>% 
  mutate(pages = str_extract(Format, "\\d+.*?p\\.|microfiche")) 

nrow(df_cln)
```

```{r}
glimpse(df_cln)
```

Write the table for manual selection

```{r}
write.csv(df_cln, file = "../metadata/exported_merged.csv")
```

# Gallica links

```{r}
biblio <- read.csv("../metadata/exported_merged.csv")
glimpse(biblio)

# fast fix for links with additional things written at the URL field
biblio <- biblio %>% 
  rename(link = Identifiant) %>% 
  mutate(link = str_remove_all(link, "[[:space:]]|\\| .*")) %>% 
  filter(str_detect(link, "^http"))

nrow(biblio)

biblio %>% 
  select(link)
```

Example

```{r}
biblio$link[1]
w <- read_html(biblio$link[1])

# extract gallica link element
w %>% 
  html_elements(".exemplaire-action-visualiser") %>% 
  html_attr("href")
```

```{r}
# fast link retrieval for fauchet
biblio <- df %>% 
  rename(link = Identifiant) %>% 
  mutate(link = str_remove_all(link, "[[:space:]]|\\| .*")) %>% 
  filter(str_detect(link, "^http"))
```

Export links

```{r}

gallica_url <- sapply(biblio$link, function(url) {
  
  print(url)
  
  url %>%
    as.character() %>%
    read_html() %>%
    html_elements(".exemplaire-action-visualiser") %>%
    html_attr("href")
  
})
```

```{r}
head(gallica_url)
```

```{r}
nrow(biblio)
length(gallica_url)

biblio <- biblio %>% mutate(link_gallica = sapply(gallica_url, paste, 
                                        collapse = " | "))
```

```{r}
glimpse(biblio)
```

Export results

```{r}
write.csv(biblio %>% select(-X), "../metadata/exported_links.csv")

# write.csv(biblio, "../metadata/fauchet.csv")
```

### 
